%%% 0bAbstract/ %%%
\chapter*{Abstract}
Trust frameworks and reputation systems are essential aspects of any online
interaction system. It helps users to evaluate the trustworthiness of
participating entities before engaging in a transaction. Therefore, the
information available about an online identity via a reputation system needs to
be correct, reliable and attack resistant. Most of the online transaction
systems have a client-server architecture with centralized data point and
governance. Thus, the data available to them are prone to both external attack
and internal modification. Therefore, this master's thesis intends to study the
use of Blockchain technology as a distributed and decentralized infrastructure
that can guarantee storage of reliable and immutable trust scores. Method of
graph properties, network flow, and graph-based algorithms are studied and
analyzed to motivate a solution. Use of smart contracts to define the
interaction between network participants and their collection and aggregation
via simple computation steps is proposed. The proposed model is applied to an
existing real dataset to demonstrate the functionality, correctness, and
usability. An interaction graph is presented to demonstrate the different
behavior of users in the network. The evaluation of the interaction graph shows
that the trust metrics are representative of user behavior in a way to be
relevant to the definition of honest and malicious interactions. Relevant
threat models that exist in current reputation systems and how the proposed
model can address them is discussed. It concludes with a discussion on
generalization and further improvements as future works. 

%Trust frameworks and reputation systems are essential aspects of any online
%interaction system. It helps users to evaluate the trustworthiness of
%participating entities before engaging in a transaction. Therefore, the
%information available about an online identity via a reputation system needs to
%be correct, reliable and attack resistant. Most of the online transaction
%systems have a client-server architecture with centralized data point and
%governance. Thus, the data available to them are prone to both external attack
%and internal modification. Therefore, this master's thesis intends to study the
%use of Blockchain technology as a distributed and decentralized infrastructure
%that can guarantee storage of reliable and immutable trust scores. Method of
%graph properties, network flow, and graph-based algorithms are studied and
%analyzed to motivate a solution. Use of smart contracts to define the
%interaction between network participants and their collection and aggregation
%via simple computation steps is proposed. The proposed model is applied to an
%existing real dataset to demonstrate the functionality, correctness, and
%usability.
%Based on the evaluation of interaction graph, results show that the
%trust metrics are representative of a trust score for the entity in question.
%The model addresses various threat models of current reputation systems and is
%supported by the results. It concludes with a discussion on generalization and
%further improvements as future works. 
